Adaptive Disk Storage for Interaction Graphs

### 2014-05-07 docs/graph-adapt/main.tex
Re-organized directory structure
updated alternative algorithm

@@

\item First, let's define a measure for the similarity between two
partitions. I think this can be the sum of the size of attributes that
they do not have in common. So, if we have partitions: abc, abd, and
abe, then abc-abd will be more similar than abc-abe, if size(d) <
size(e).

@@

>>>>

\paragraph{First proposal}

@@

\item First, let's define a measure for the similarity between two
partitions. I think this can be the sum of the size of attributes that
they do not have in common. So, if we have partitions: abc, abd, and
abe, then abc-abd will be more similar than abc-abe, if size(d) $<$
size(e).

@@

\paragraph{Second proposal}

\item We keep a mapping of queries to blocks and frequencies.

\item If the storage cost is above some threshold, then we get the queries with
  the lowest frequencies, and combine their blocks. We also add the frequencies,
  so we are combining the blocks that are least likely to be accessed.

\item We repeat until we are below the storage threshold.

\begin{algorithm}[h]
\scriptsize
\caption{Alternative algorithm for partitioning blocks into sub-blocks with overlapping attributes.}
\label{alg:overlappingP2}
\SetKwFunction{Enqueue}{Enqueue}
\SetKwFunction{Dequeue}{Dequeue}

\KwData{$B$: block, $Q$: set of queries}
$\mathcal{P}(B) \leftarrow \emptyset;$  \tcp*{Sub-blocks;}
$pq \leftarrow \emptyset;$  \tcp*{priority queue;}

\For(\tcp*[f]{Every query gets its own sub-block}){$q \in Q$}{ 
 $\mathcal{P}(B) = \mathcal{P}(B) \cup q.A$ \;
 \Enqueue{$pq,\mathcal{P}(B), f(\mathcal{P}(B))$}\tcp*{put blocks in the queue;}
}
\While(\tcp*[f]{While storage exceeds threshold}){$H(\mathcal{P}, B) \geq
  \text{max}$}{  
  $x \leftarrow $ \Dequeue{$pq$}\;
$y \leftarrow $ \Dequeue{$pq$}\tcp*{remove the two minimum;}
  \Enqueue{$pq,x \cup y, f(x) + f(y)$}\tcp*{combine and insert;}    
    }

\For(\tcp*[f]{The elements in the queue are our partition}){$p \in pq$}{ 
  $ \mathcal{P}(B)  \leftarrow \mathcal{P}(B) \cup p$ \;
}
\Return $ \mathcal{P}(B)$  \tcp*{Final set of sub-blocks}
\end{algorithm}
